A Short Guide to Anyons and Modular Functors

### 2016-09-25 guide.tex
commit edits

\subsub{Curve diagram.}
We next study maps from standard surfaces to arbitrary surfaces.
%\cggb{I was a bit confused what this means. Maps means
%between surfaces with the same holes and base points, right?
%So then don't we only care about maps from standard
%surfaces to standard surfaces? Is it maybe more like maps
%from equatorial curve diagrams on standard surfaces to arbitrary curve
%diagrams on standard surfaces that we want?}
The reader should think of this as akin to choosing a basis
for a vector space.
The set of all maps from $\StdM$ 
to a surface $N$ will be denoted as $\Hom(\StdM, N).$ 
We call each such map a \emph{curve diagram},
or more specifically, a curve diagram on $N$.
The reason for this terminology is that we can reconstruct (up to isotopy)
any map $f:\StdM\to N$ from
the restriction of $f$ to the equator of $\StdM.$ % XXX XXX XXX \cggb{citation? or obvious?}
In other words, we can uniquely specify any map
$f:\StdM\to N$ by indicating the action of
$f$ on the equator. We take full advantage of this
fact in our notation: any figure of a surface
with a ``green line'' drawn therein is actually notating a 
diffeomorphism, not a surface!

>>>>

\subsub{Curve diagram.}
We next study maps from standard surfaces to arbitrary surfaces.
%\cggb{I was a bit confused what this means. Maps means
%between surfaces with the same holes and base points, right?
%So then don't we only care about maps from standard
%surfaces to standard surfaces? Is it maybe more like maps
%from equatorial curve diagrams on standard surfaces to arbitrary curve
%diagrams on standard surfaces that we want?}
The reader should think of this as akin to choosing a basis
for a vector space.
The set of all maps from $\StdM$ 
to a surface $N$ will be denoted as $\Hom(\StdM, N).$ 
We call each such map a \emph{curve diagram},
or more specifically, a curve diagram on $N$.
The reason for this terminology is that we can reconstruct (up to isotopy)
any map $f:\StdM\to N$ from
the restriction of $f$ to the equator of $\StdM.$
In other words, we can uniquely specify any map
$f:\StdM\to N$ by indicating the action of
$f$ on the equator.
(This reconstruction works because a simple closed curve on a sphere cuts 
the sphere into two discs.)
We take full advantage of this
fact in our notation: any figure of a surface
with a ``green line'' drawn therein is actually notating a 
diffeomorphism, not a surface!
